FinalManuscript_DISCS_UG

### 2019-03-02 parts/02_relatedliterature_05partiallyhomomorphic.tex
WIP cryptosystem RRL
working on cryptosystem RRL

In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.

\subsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

\subsubsection{Key Generation}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

@@

\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
\end{align*}

%In order to implement some image operations covered in this study, we require the exponentiation %of ciphertexts to integer powers, i.e. we require a function $f$ so that
%\begin{align*}
%	D(f(E(m))) = m^k\bmod n
%\end{align*}
%for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

%This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
%\begin{align*}
%	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
%	&= m^{k+2}\bmod n
%\end{align*}

%We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem. Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity. The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

@@

\subsubsection{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
\end{align*}

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^kr) \bmod{n}\\
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
\end{proof}

%\subsection{DGK Comparison Protocol}
%The DGK system was primarily developed as part of a comparison protocol, a protocol which allows
%It is known that $E(m)^{v_pv_q} \bmod n = 1$ if and only if $m=0$. This allows

%\subsection{The Benaloh cryptosystem}
%The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$. It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}. We present here a corrected version by Fousse, et al. \cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.

%\subsubsection{Benaloh Cryptosystem Description}
%We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
%\begin{itemize}
%  \item $r$ divides $(p-1)$;
%  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
%  \item $\mathrm{gcd}(r,q-1)=1$.
%\end{itemize}
%Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
%\begin{itemize}
%  \item $y^{\phi/r}\neq 1 \bmod n$;
%  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
%\end{itemize}
%We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

%The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
%\begin{align*}
%  E(m) = y^m \cdot u^r \mod{n},
%\end{align*}
%where $u$ is a random integer in $\mathbb{Z}_n^*$.

%The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
%\begin{align*}
%  D(c) = \log_x{c^{\phi/r}} \mod n
%\end{align*}
%where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.

%Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small. For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.

%\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
%Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
%For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
%\begin{description}
%  \item[Additive homomorphism]
%  \begin{align*}
%    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
%    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
%  \end{align*}
%  \item[Multiplicative homomorphism]
%  \begin{align*}
%    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
%  \end{align*}
%\end{description}

%As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
%\begin{proof}
%  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
%  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
%  \begin{align*}
%    (y^m \cdot u^r \bmod{n})^k\bmod n
%    &= (y^m \cdot u^r)^k \bmod{n}\\
%    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
%    &= y^{km} \cdot (u^k)^r \bmod{n}\\
%    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
%  \end{align*}
%  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
%  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
%  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
%\end{proof}

\subsection{General Exponentiation Protocol for Paillier and DGK}
\label{ssec:exponentiationprotocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
\end{itemize}

This can be extended to arbitrary integer powers.
Suppose Alice encrypts and integer $x$, and Bob has $E(x), E(x^2), ..., E(x^{n-1})$ and wants to obtain $E(x^n)$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice sends $E((x+r)^n)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E((x+r)^n) - E\left(\sum_{i=1}^{n-1}{\binom{n}{i}x^ir^{n-i}}\right),
	\end{align*}
	which evaluates to $E(x^n)$ by the binomial theorem.
\end{itemize}

>>>>

In this section, we will present two classical partially homomorphic cryptosystems (PHEs) which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar. We will then show how these PHEs may be adapted for secure floating-point computation.

\subsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.

\subsubsection{Key Generation}
We choose two large primes $p$ and $q$, and set $n = pq $ and $ \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
We then define $L\left(x\right)$ to be the largest integer $v$ greater than zero such that $x-1 \geq vn$.
Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
We define the public key as $(g,n)$ and the private key as $(p,q)$.

@@

\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (add a plaintext constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (ciphertext addition)}\\
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (multiply a plaintext constant)}
\end{align*}

@@

\subsubsection{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (add a plaintext constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (ciphertext addition)}\\
    D(E(m_1)^k)= km_1\bmod u & \text{ (multiply a plaintext constant)}
\end{align*}

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^{kr}) \bmod{n}
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
\end{proof}

\subsection{Floating-Point Arithmetic using PHEs}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHEs may be extended to a system which allows for secure floating-point computation.

In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE, respectively.

\subsubsection{Extension to Floating-Point Numbers}
\label{sec:fp_operations}
We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend Paillier and DGK to floating-point numbers.

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. We define the corresponding FP number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E\left(c\right)=E\left(a+b\right)$ we compute
	\begin{align*}
		E\left(m_c\right) &= 
		\begin{cases}
			E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
			E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
		\end{cases}, \\
		e_c &= 
		\begin{cases}
			e_a & \text{if } e_a \leq e_b \\
			e_b & \text{if } e_a > e_b
		\end{cases}.
	\end{align*}
  \item[Scalar multiplication.]
    To compute $E\left(c\right) = E\left(ab\right)$, where $a$ and $E\left(b\right)$ are known (i.e., $m_a$ is not encrypted), we compute
    \begin{align*}
      E\left(m_c\right) &= m_a \otimes E\left(m_b\right),\\
      e_c &= e_a + e_b.
    \end{align*}
\end{description}

\subsubsection{Secure Division}
We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.

Suppose Bob has $E\left(x\right)$ and $E\left(y\right)$ and wants to obtain $E\left(x/y\right)$ without exposing the value of either variable.
\begin{itemize}
	\item Bob first selects a random non-zero number $r$ and computes $E\left(rx\right)$ and $E\left(ry\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(rx\right)$ and $E\left(ry\right)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
	\item Alice encrypts and sends $E\left(x/y\right)$ to Bob.
\end{itemize}

\subsubsection{Secure Exponentiation}
\label{ssec:exponentiationprotocol}
 We can use the following two-party scheme, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, in order to perform secure exponentiation.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
	\begin{align*}
		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
		&= \frac{1}{2}E\left(2xy\right)\\
		&= E\left(xy\right).
	\end{align*}
\end{itemize}

By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived.

### 2019-03-02 parts/02_relatedliterature_06fullyhomomorphic.tex
WIP cryptosystem RRL
working on cryptosystem RRL

We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

\subsection{The Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{Z}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2.
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used:
\begin{align*}
	R(c(x)) = c(x) \bmod R_k.
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.

@@

The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper. For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

>>>>

We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems. 
Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.

\subsection{DGHV Cryptosystem}
In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}. This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.

The DGHV cryptosystem encrypts single bits as integer ciphertexts. XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts. When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.

A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.

For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and

@@

For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

### 2019-03-02 parts/03_methodology_02nonlinearintensitytransformations.tex
WIP cryptosystem RRL
working on cryptosystem RRL

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.

>>>>

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in % Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix %\ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
